---
title: "hw2"
Author: "hw2765"
output: html_document
---

Problem1

```{r}
library(tidyverse)
getwd()
library(readxl)
```

```{r}
trashwheel = read_xlsx("./Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "Mr. Trash Wheel", range = cell_cols("A:N")) %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
view(trashwheel)

Precip_2017 = read_excel("./Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2017 Precipitation", skip = 1, ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2017)  %>%
  relocate(year)
view(Precip_2017)

Precip_2018 = read_excel("./Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2018 Precipitation", skip = 1, ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2018)  %>%
  relocate(year)
view(Precip_2018)

Precip = bind_rows(Precip_2017, Precip_2018) %>%
mutate(month = month.name[month])
nrow(Precip)
sum(pull(Precip_2018, total))
sb_2017= filter(trashwheel, year==2017)
median(pull(sb_2017, sports_balls))
```
The number of observation in total consists of 24 observations.
The total precipitation in 2018 is 70.33 inches
The median of sports ball in a dumpster in 2017 is 8

Problem 2

```{r}
nyctransit = read_csv(file="./NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>%
janitor::clean_names() %>%
select(line, station_name, station_latitude, station_longitude, route1:route11, entrance_type, entry, vending, ada) %>%
mutate(entry = recode(entry,"YES"=TRUE,"NO"=FALSE))
names(nyctransit)
```
This data sets contains data of nyc subway system，19 variables in total:
"line""station_name""station_latitude""station_longitude""route1""route2""route3"         "route4""route5""route6""route7""route8""route9""route10""route11""entrance_type"   "entry""vending""ada"  

How many distinct stations are there? 

```{r}
dstation= distinct(select(nyctransit,station_name,line,ada))
nrow(dstation)
```
465 distinct stations

How many stations are ADA compliant?

```{r}
nrow(filter(dstation,ada==TRUE))
```
84 stations are ADA compliant

What proportion of station entrances / exits without vending allow entrance?

```{r}
nrow(filter(nyctransit,vending=="NO",entry==TRUE))/nrow(filter(nyctransit,vending=="NO"))
```
37.70% of station entraces/exits without vending allow entrance

```{r}
nyctransit_char = mutate(nyctransit, route8 = as.character(route8),  route9 = as.character(route9), route10 = as.character(route10), route11 = as.character(route11))
nyctransit_droute = pivot_longer(nyctransit_char,
    route1:route11,
    names_to = "route_num",
    values_to = "route_name"
  ) %>%
  drop_na()
nyctransit_droute
```
How many distinct stations serve the A train? Of the stations that serve the A train, how many are ADA compliant?

```{r}
a_dstation = distinct(select(nyctransit_droute,station_name,line,route_name,ada)) %>%
  filter(route_name=="A")
nrow(a_dstation)
nrow(filter(a_dstation, ada==TRUE))
```
60 distinct stations serve the A train，which 17 of them are ADA compliant


Problem 3

```{r}
library(tidyr)
polsmonth = read_csv(file = "./fivethirtyeight_datasets/pols-month.csv") %>%
  janitor::clean_names() %>%
  drop_na() %>%
  separate(mon, into = c("year", "month", "day"), sep = "-" ) %>%
  mutate(month = month.name[as.integer(month)]) %>%
  mutate(president = case_when(prez_gop == 1 ~ "gop", prez_dem == 1 ~ "dem")) %>%
  select(year, month, gov_gop, sen_gop, rep_gop, gov_dem, sen_dem, rep_dem, president)
view(polsmonth)
```

